---
title: "AS3-3: 美國的人口統計和就業資料"
author: "第16組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset

__§ 1.1__ How many interviewees are in the dataset?
```{r}
# 131302位
setwd("~/Desktop/unit03/data")
CPS<- read.csv("CPSData.csv")
nrow(CPS)
```

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it.
```{r}
# Educational and health services 受訪者最多（屏除NA值），因為在社會中服務業的比例也最高
summary(CPS$Industry)
```

__§ 1.3__ Which state has the fewest interviewees?
```{r}
# New Mexico (但NA值最多)，位於美國中南部，農業產業居多，地廣人希，受訪者就比較少
head(sort(table(CPS$State)))
```

Which state has the largest number of interviewees?
```{r}
# California，人口本來就比較多，服務業也較發達
sort(table(CPS$State)) %>% tail()
```

__§ 1.4__ What proportion of interviewees are citizens of the United States?
```{r}
# 0.942194，受訪者幾乎全是美國公民
prop.table(table(CPS$Citizenship))
prop.table(table(CPS$Citizenship=="Non-Citizen"))
```

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.) 

+ American Indian
+ Asian
+ cBlack
+ Multiracial
+ Pacific Islander
+ White

```{r}
# American Indian、Black、Multiracial、White為同時是西班牙裔又超過250人的種族
table(CPS$Race,CPS$Hispanic)
```

<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode
+ Age
+ Married
+ Sex
+ Education
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus
+ Industry

```{r}
# Married、Education、EmploymentStatus、MetroAreaCode、Industry有遺漏值，可能比較難分類，自我認同有問題
colSums(is.na(CPS))
```

__§ 2.2__  Which is the most accurate:

+ The Married variable being missing is related to the Region value for the interviewee.
+ The Married variable being missing is related to the Sex value for the interviewee.
+ The Married variable being missing is related to the Age value for the interviewee. 
+ The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
# 由下可知Age的精準度較高
lapply(CPS[c('Region','Sex','Age','Citizenship')], 
       function(x) table(is.na(CPS$Married), x))
```


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state).
```{r}
# 2個地方沒捷運，Alaska和Wyoming，這兩個地方偏僻到蓋捷運只有北極熊和美洲野牛會搭
table(is.na(CPS$MetroAreaCode), CPS$State)
```

How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state.
```{r}
# 3個地方是所有人都有捷運搭，別是Columbia、New Jersey、Rhode Island，因為土地面積比較小
```

__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area?
```{r}
# Midwest有捷運的比例最低，因為美國中部都是國家公園
sort(tapply(is.na(CPS$MetroAreaCode), CPS$Region, mean))
```

__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%?
```{r}
# Wisconsin
head(sort(abs(0.3 - tapply(is.na(CPS$MetroAreaCode), CPS$State, mean))))
```

Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan?
```{r}
# Montana，排除掉完全沒捷運的地方，倒數第三州為Montana，搞農業的
tail(sort(tapply(is.na(CPS$MetroAreaCode), CPS$State, mean)))
```

<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap?
```{r}
# 271筆
setwd("~/Desktop/unit03/data")
MAC <- read.csv("MetroAreaCodes.csv")
nrow(MAC)
```

How many observations (codes for countries) are there in CountryMap?
```{r}
# 149筆
setwd("~/Desktop/unit03/data")
CC <- read.csv("CountryCodes.csv")
nrow(CC)
```

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?
```{r}
# MetroArea
CPS <- merge(CPS, MAC, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
```

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
# 34238
sum(is.na(CPS$MetroArea))
```

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?
```{r}
# New York-Northern New Jersey-Long Island, NY-NJ-PA
tail(sort(table(CPS$MetroArea)))
```

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity?
```{r}
# Laredo, TX，這兩個地方的西班牙裔受訪者較多
tail(sort(tapply(CPS$Hispanic,CPS$MetroArea,mean)))
```

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.
```{r}
# 4個地方，Vallejo-Fairfield, CA、San Jose-Sunnyvale-Santa Clara, CA、San Francisco-Oakland-Fremont, CA、Honolulu, HI
tail(sort(tapply(CPS$Race == "Asian", CPS$MetroArea, mean)))
```

__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma.
```{r}
#  Iowa City, IA的人有捷運搭而且學歷較低
head(sort(tapply(CPS$Education == "No high school diploma", CPS$MetroArea, mean, na.rm=T)))
```


<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation?
```{r}
# Country
CPS = merge(CPS, CC, by.x="CountryOfBirthCode", by.y="Code", all.x=TRUE)
```

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
# 176個受訪者不想表態自己的國家
sum(is.na(CPS$Country))
```

__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth?
```{r}
# Mexico為美國最大移入國，所以川普才要蓋牆，但如果將墨西哥視為北美，則最大移入國為菲律賓
tail(sort(table(CPS$Country)))
```

__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States? 
```{r}
# 0.3087住在NY-NJ-PA的人出生地非美國
area <- "New York-Northern New Jersey-Long Island, NY-NJ-PA"
mean(CPS$Country[CPS$MetroArea==area] != "United States", na.rm=T)
```

__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India? 
```{r}
# New York-Northern New Jersey-Long Island, NY-NJ-PA有最多人印度裔
tail(sort(tapply(CPS$Country == 'India', CPS$MetroArea, sum, na.rm=T)))
```

In Brazil?
```{r}
# Boston-Cambridge-Quincy, MA-NH有最多巴西裔
tail(sort(tapply(CPS$Country == 'Brazil', CPS$MetroArea, sum, na.rm=T)))
```

In Somalia?
```{r}
# Minneapolis-St Paul-Bloomington, MN-WI有最多索馬利亞裔
tail(sort(tapply(CPS$Country == 'Somalia', CPS$MetroArea, sum, na.rm=T)))
```

<br><br><br>
