---
title: 第三單元：(A)資料檢視與繪圖
author: 中山大學管理學院 卓雍然
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這段程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(magrittr)
```
<hr>

###【CASE 1】世界衛生組織資料集 WHO Dataset

##### 載入資料 Loading Data
```{r}
WHO = read.csv("data/WHO.csv")
```

##### 資料總覽 Data Summary
```{r}
summary(WHO)
```

##### 基本資料檢視 Basic Data Examination
**15歲以下人口比率**
```{r}
mean(WHO$Under15)
sd(WHO$Under15)
summary(WHO$Under15)
```

**15歲以下人口比率最低的國家**
```{r}
which.min(WHO$Under15)
WHO$Country[86]
WHO$Country[which.min(WHO$Under15)]
```

**15歲以下人口比率最高的國家**
```{r}
which.max(WHO$Under15)
WHO$Country[124]
WHO$Country[which.max(WHO$Under15)]
```
<br>

##### 點狀圖 Scatterplot
```{r}
plot(WHO$GNI, WHO$FertilityRate)
abline(v=10000, h=2.5, col='pink')
```

##### 資料篩選 Subsetting
```{r}
Outliers = subset(WHO, GNI > 10000 & FertilityRate > 2.5) 
nrow(Outliers)
Outliers[c("Country","GNI","FertilityRate")]
```
<br>

##### 直方圖 Histogram
```{r}
hist(WHO$CellularSubscribers)
```
<br>

##### 盒狀圖 Boxplot
```{r}
boxplot(WHO$LifeExpectancy ~ WHO$Region, las=2)
```

```{r}
boxplot(WHO$LifeExpectancy ~ WHO$Region, 
        xlab = "", ylab = "Life Expectancy", 
        main = "Life Expectancy of Countries by Region")
```

##### 分類數量功能 `table()`
```{r}
table(WHO$Region)
```
<br>

##### 分類統計功能 `table()`
```{r}
tapply(WHO$Over60, WHO$Region, mean)
tapply(WHO$LiteracyRate, WHO$Region, min)
tapply(WHO$LiteracyRate, WHO$Region, min, na.rm=TRUE)
```
<br><br><hr>

###【CASE 2】食物成分資料 WHO Dataset

##### 載入、檢視資料 Video2 - Reading in the Dataset
```{r}
USDA = read.csv("data/USDA.csv")
summary(USDA)
```
<br>

##### 簡單資料分析 Video 3 - Basic Data Analysis
**鹽分含量：** 當資料很大的時候
```{r}
USDA$Sodium
```

**鹽分含量最高的食物**
```{r}
# Finding the index of the food with highest sodium levels
which.max(USDA$Sodium)
# Get the name of the food with highest sodium levels
USDA$Description[265]
```

**高鹽食物**
```{r}
# Create a subset of the foods with sodium content above 10,000mg
HighSodium = subset(USDA, Sodium>10000)
# Count the number of rows, or observations
nrow(HighSodium)
# Output names of the foods with high sodium content
HighSodium$Description
```

**魚子醬**
```{r}
# Finding the index of CAVIAR in the dataset
match("CAVIAR", USDA$Description)
# Find amount of sodium in caviar
USDA$Sodium[4154]
# Doing it in one command!
USDA$Sodium[match("CAVIAR", USDA$Description)]
```

**統計量**
```{r}
# Summary function over Sodium vector
summary(USDA$Sodium)
# Standard deviation
sd(USDA$Sodium, na.rm = TRUE)
```
<br>

##### 基本繪圖 Video 4 - Plots

**點狀圖：蛋白質 vs. 脂肪**
```{r}
# Scatter Plots
plot(USDA$Protein, USDA$TotalFat)
# Add xlabel, ylabel and title
plot(USDA$Protein, USDA$TotalFat, 
     xlab="Protein", ylab = "Fat", 
     main = "Protein vs Fat", col = "red")
```

**直方圖：維他命C**
```{r}
# Creating a histogram
hist(USDA$VitaminC, xlab = "Vitamin C (mg)", main = "Histogram of Vitamin C")

# Add limits to x-axis
hist(USDA$VitaminC, xlab = "Vitamin C (mg)", 
     main = "Histogram of Vitamin C", xlim = c(0,100))

# Specify breaks of histogram
hist(USDA$VitaminC, xlab = "Vitamin C (mg)", 
     main = "Histogram of Vitamin C", xlim = c(0,100), breaks=100)

hist(USDA$VitaminC, xlab = "Vitamin C (mg)", 
     main = "Histogram of Vitamin C", xlim = c(0,100), breaks=2000)
```

**盒狀圖：糖分**
```{r}
# Boxplots
boxplot(USDA$Sugar, ylab = "Sugar (g)", main = "Boxplot of Sugar")
```
<br>

##### 定義新欄位 Video 5 - Adding a variable
```{r}
# Creating a variable that takes value 1 if the food has higher sodium
HighSodium = as.numeric(USDA$Sodium > mean(USDA$Sodium, na.rm=TRUE))

# Adding the variable to the dataset
USDA$HighSodium = as.numeric(USDA$Sodium > mean(USDA$Sodium, na.rm=TRUE))

# Similarly for HighProtein, HigCarbs, HighFat
USDA$HighCarbs = as.numeric(USDA$Carbohydrate > mean(USDA$Carbohydrate, na.rm=TRUE))

USDA$HighProtein = as.numeric(USDA$Protein > mean(USDA$Protein, na.rm=TRUE))

USDA$HighFat = as.numeric(USDA$TotalFat > mean(USDA$TotalFat, na.rm=TRUE))
```
<br>

##### 分類計數與分類統計量 Video 6 - Summary Tables
<p class="qiz">
<span style="font-size:24px">`r "\U1F4DD"` 練習：</span><br>
以下的運算式分別代表什麼意思 ...<br>
&emsp; ■ `table(USDA$HighSodium)`<br>
&emsp; ■ `table(USDA$HighSodium, USDA$HighFat)`<br>
&emsp; ■ `tapply(USDA$Iron, USDA$HighProtein, mean, na.rm=TRUE)`<br>
&emsp; ■ `tapply(USDA$VitaminC, USDA$HighCarbs, max, na.rm=TRUE)`<br>
&emsp; ■ `tapply(USDA$VitaminC, USDA$HighCarbs, summary, na.rm=TRUE)`<br>
</p class="qiz">

<span style="font-size:24px">`r "\U1F4CB"`</span>: 低、高鹽食品的個數
```{r}
table(USDA$HighSodium)
```
<br>

<span style="font-size:24px">`r "\U1F4CB"`</span>: 答案
```{r}
table(USDA$HighSodium, USDA$HighFat)
```
<br>

<span style="font-size:24px">`r "\U1F4CB"`</span>: 答案
```{r}
tapply(USDA$Iron, USDA$HighProtein, mean, na.rm=TRUE)
```
<br>

<span style="font-size:24px">`r "\U1F4CB"`</span>: 答案
```{r}
tapply(USDA$VitaminC, USDA$HighCarbs, max, na.rm=TRUE)
```
<br>

<span style="font-size:24px">`r "\U1F4CB"`</span>: 答案
```{r}
tapply(USDA$VitaminC, USDA$HighCarbs, summary, na.rm=TRUE)
```





